Fail Faster

### 2025-03-18 paper/paper.tex
lol

\section{Evaluation}
\label{section:eval}
\begin{itemize}
  \item \textbf{RQ1}: Do generators written using \name run faster than those written using base quickcheck?
  \item \textbf{RQ2}: Do performance speedups translate to better bug-finding ability?
  \item \textbf{RQ3}: Does our technique generalize to other strict functional languages?
\end{itemize}

>>>>

\section{Evaluation}
\label{section:eval}

\jwc{Initial section here about eval}

\begin{itemize}
  \item \textbf{RQ1}: Do generators written using \name run faster than those written with regular generator combinators?
  \item \textbf{RQ2}: Do performance speedups translate to better bug-finding ability?
  % \item \textbf{RQ3}: Does our technique generalize to other strict functional languages?
\end{itemize}
